---
title: "Introduction"
author: "DJ Forbes"
date: 2019-12-06T21:13:14-05:00
publishdate: 2019-12-06T21:13:14-05:00
categories: ["Introduction"]
tags: ["R Markdown", "plot", "regression"]
slug: "intro-practical-r"
output:
  blogdown::html_page:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)

# include a twitter card like this:
# blogdown::shortcode('tweet', '852205086956818432')
# must be inside a chunk

# IMPORTANT:
# Every blog post you write should aim to solve a problem, such as by educating, informing, or 
# entertaining someone.

```

# Introduction

Are you struggling to learn R so you can create banging data visualizations and produce data science projects that add value?  

> You are not alone.  Analyzing data is now common to a lot of professions that may not have any background in programming or computer science.  

Are you full of excitement for your new R project but finding it difficult to quickly achieve the results you want and need?

> Coming from a background in other programming languages may be problematic because R does some things a little bit differently.  

Are you taking a course in R and finding that you can't keep up with the class and need some background?

Or are you just interested in learning more about R and what R can do?

> I would like to help you do more with R.  I want to inspire you to create your own data visualizations, master data science, or develop your own data stories.  I want to share practical R tips, tricks, and complete projects with you.  

Topics covered include anything having to do with R.  This blog will focus especially on 

* new R packages
* geospatial analysis using R
* GIS and mapping with R
* statistics with R
* data science with R. 

> On occasion there may even be posts focused on NBA basketball statistics ([#GoSpursGo!](https://www.nba.com/spurs/)).

Using both example data and "real" data, I’ll be sharing code like this:

```{r iris}
data(iris)
str(iris)

```

# Data Visualization

I’ll be sharing data visualizations as well, including mapping and GIS with R.  

See Figure \@ref(fig:hist) for an example:

```{r hist, fig.cap="A histogram of Sepal Width measurements in Edar Anderson's Iris Data.", tidy=FALSE}
hist(iris$Sepal.Width, 
     main = "Histogram of Sepal Width", 
     xlab = "Sepal Width", 
     xlim = c(2,5), 
     col = rcartocolor::carto_pal(2,"Fall"),
     freq = TRUE)
```

# Data Science

Together we will explore "doing" data science with R.  See Figure \@ref(fig:irisscattermatrix).

```{r irisscattermatrix}
pairs(iris[1:4], main = "Scatterplot Matrix (Iris Data)", pch = 21, bg = c("red", "green3", "blue")[unclass(iris$Species)])

```

